\chapter*{Acknowledgment}
\addcontentsline{toc}{section}{\textbf{Acknowledgment}}

\vspace{0.5cm}

Before presenting the work carried out during this end-of-study internship, I would like to express my sincere gratitude to all the people who contributed, directly or indirectly, to the success of this project.

\vspace{0.3cm}

I would first like to thank \textbf{Theodo Morocco} for the trust it placed in me by welcoming me within its teams. This internship gave me the opportunity to grow in a stimulating, demanding, and deeply human professional environment.

\vspace{0.3cm}

I extend my warmest thanks to my company supervisor, \textbf{Mr. Othmane Kinane}, for his guidance, his availability, and the quality of the feedback he provided throughout this experience. My gratitude also goes to \textbf{Yassine Ghazouan}, Tech Lead, and \textbf{Hamza Berraho}, Project Manager, whose technical insight and clear vision constantly steered the project in the right direction. I am also sincerely grateful to my coach, \textbf{Abdelaziz Afriad}, for his guidance and his mentorship throughout this journey, and for helping me become more integrated into this new environment.

\vspace{0.3cm}

I am equally grateful to my teammates, \textbf{Mohammed Bourhym} and \textbf{Ismail Drissi}, for their collaboration, their generosity in sharing knowledge, and the team spirit that made every challenge easier to overcome.

\vspace{0.3cm}

I would also like to express my deep appreciation to my academic supervisor, \textbf{Pr. Abdelmajid Bousselham}, for his attentive follow-up, his valuable advice, and his rigor, which greatly contributed to the quality of this report.

\vspace{0.3cm}

Finally, I address my thanks to the entire teaching staff of the \textbf{Department of Mathematics and Computer Science}, as well as to all those who, through their support and encouragement, accompanied me throughout these years of study.

\clearpage
